A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-01-29 paper.tex
reference to fig:extended

The tree is first extended to the maximum bound with edges that are labeled
with arbitrary opponent actions (Algorithm~\ref{alg:bounded}, line 14) as shown
in Figure~\ref{}. Then copies of state and action variables are introduced for
each node in tree and opponent action variables for each edge.  Opponent
actions are set to $\textsc{action}(e)$, the action that labels the edge of the
tree $e$. The new state and action variables are connected to the successor
nodes (\textsc{succ}) by an encoding transition relation and constrained to the
winning condition of the player.

>>>>

The tree is first extended to the maximum bound with edges that are labeled
with arbitrary opponent actions (Algorithm~\ref{alg:bounded}, line 14) as shown
in Figure~\ref{fig:extended}. Then copies of state and action variables are introduced for
each node in tree and opponent action variables for each edge.  Opponent
actions are set to $\textsc{action}(e)$, the action that labels the edge of the
tree $e$. The new state and action variables are connected to the successor
nodes (\textsc{succ}) by an encoding transition relation and constrained to the
winning condition of the player.
